(ref:centralities-plot) The centrality scores for each node in our network plotted.
```{r centralities-plot, fig.cap = "(ref:centralities-plot)", echo = TRUE}
centralities_plot <- snafun::plot_centralities(
  graph,
  measures = c("betweenness", "closeness", "degree", "eccentricity"), 
  directed = TRUE,
  mode = "all",
  k = 3,
  rescaled = FALSE
)
```

(ref:indegree-plot) The indegree plotted for each node in the network
```{r indegree-plot, fig.cap = "(ref:indegree-plot)", fig.height = 8, echo = TRUE}
# Plotting indegree for each node 
# Coloring each node based on its sentiment
igraph::V(graph)$color <- "orange"
igraph::V(graph) [ sentiment == 'negative' ]$color <- "#F25F5C"
igraph::V(graph) [ sentiment == 'positive' ]$color <- "#9DBF9E"
igraph::V(graph) [ sentiment == 'neutral' ]$color <- "orange"

my_df <- data.frame(
  igraph::get.vertex.attribute(graph, name = "id"), 
  igraph::get.vertex.attribute(graph, name = "color"),
  1:324
  )

v_degree <- igraph::degree(graph, mode = "in")

my_df <- cbind(my_df, v_degree)

names(my_df) <- c("id", "color", "new_id", "degree")

plot(y = my_df$new_id, 
     x = my_df$degree,
     xlab = "indegree",
     ylab ="",
     col = my_df$color,
     type = "b",
     pch = 16)

# Adding a legend
legend("topright", # Location of the legend. Change as needed.
       legend = c("Negative: 253", 
                  "Positive: 6", 
                  "Neutral: 62"),  # Labels in the legend
       col = c("#F25F5C", 
               "#9DBF9E", 
               "orange"), # Colors corresponding to labels
       pch = 16)
```

(ref:outdegree-plot) The outdegree plotted for each node in the network
```{r outdegree-plot, fig.cap = "(ref:outdegree-plot)", fig.height = 8, echo = TRUE}
# Plotting outdegree for each node 
# Coloring each node based on its sentiment
igraph::V(graph)$color <- "orange"
igraph::V(graph) [ sentiment == 'negative' ]$color <- "#F25F5C"
igraph::V(graph) [ sentiment == 'positive' ]$color <- "#9DBF9E"
igraph::V(graph) [ sentiment == 'neutral' ]$color <- "orange"

my_df <- data.frame(
  igraph::get.vertex.attribute(graph, name = "id"), 
  igraph::get.vertex.attribute(graph, name = "color"),
  1:324
  )

v_degree <- igraph::degree(graph, mode = "out")

my_df <- cbind(my_df, v_degree)

names(my_df) <- c("id", "color", "new_id", "degree")

plot(y = my_df$new_id, 
     x = my_df$degree,
     xlab = "outdegree",
     ylab ="",
     col = my_df$color,
     type = "b",
     pch = 16)

# Add a legend
legend("topright", # Location of the legend
       legend = c("Negative: 253", 
                  "Positive: 6", 
                  "Neutral: 62"), # Labels in the legend
       col = c("#F25F5C", 
               "#9DBF9E", 
               "orange"), # Colors corresponding to labels
       pch = 16)
```

# ERGM Results \
We display the results of the different models we ran as well as the diagnostics for model 5.\
(ref:ergm-results-plot) Boxplots showing the terms SEs for the different model configurations.
```{r ergm-results-plot, echo = TRUE, fig.height=7, warning = FALSE, message = FALSE} 
texreg::plotreg(models)
```
\newpage

## Model Diagnostics of model 5 \
(ref:mcmc-diagnostics) The MCMC diagnostics for model 5.
```{r mcmc-diagnostics, echo = TRUE, results = 'asis', include = TRUE, fig.height=8, fig.align='center', fig.cap="(ref:mcmc-diagnostics)"}
# Plotting MCMC diagnostic
model_5 <- models$model_5
par(mai=c(.6,0.3,.4,0.3), omi=c(.1,.1,.1,.1)) # setting margins due to error

ergm::mcmc.diagnostics(
  model_5,
  which = c("plots")
  )

```
\newpage

## Goodness of Fit of model 5 \
(ref:gof-model5) The plot below shows the Goodness of Fit statistics for model 5
```{r gof-model5, echo = FALSE, fig.cap="(ref:gof-model5)"}
plot(model_5.gof)
```

